PM Mungbean meta-analysis

### 2019-06-21 03_Preliminary_analysis.Rmd
Corrected code to make loop of density plots, one for each fungicide work.

summarise()
levels(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20)))

@@

unique(
PM_MB_means1 %>%
   group_by(Fungicide) %>%
   filter(n() >= 5) %>%
   select(days_from_1st))

PM_MB_means1 %>%
   group_by(Fungicide) %>%
   filter(n() >= 5) %>%
ggplot(aes(prop_YG))+
   geom_density(aes(fill = cut(spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(spray_diff, c(1,2,7,10,12,20))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.2,0.55))
#__________________________________________________________________________________________________________
levels(factor(PM_MB_means$Fungicide))
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == "Sulphur" |
             Fungicide == "Sulphur (SC)" |
             Fungicide == "Sulphur (Ultra SC)" |
             Fungicide == "Sulphur (WP)")
unique(PM_MB_means2$spray_diff)
ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.3,0.6))
Chemical <- c("Amistar","Carbendazim","Tebeconazole", "propiconazole")
levels(factor(PM_MB_means$Fungicide))
for(Chem in Chemical){
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == Chem)
cat(Chem)
cat(unique(PM_MB_means2$spray_diff))
p1 <- ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title=paste(Chem,"Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")))+
   scale_x_continuous(limits = c(-0.3,0.6))
print(p1)
Sys.sleep(10)
}
```

>>>>

@@

# unique(
# PM_MB_means1 %>%
#    group_by(Fungicide) %>%
#    filter(n() >= 5) %>%
#    select(days_from_1st))
# 
# 
# PM_MB_means1 %>%
#    group_by(Fungicide) %>%
#    filter(n() >= 5) %>%
# ggplot(aes(prop_YG))+
#    geom_density(aes(fill = cut(spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
#    geom_vline(aes(xintercept = 0), size =0.5)+
#    facet_grid(rows = vars(cut(spray_diff, c(1,2,7,10,12,20))), cols = vars(Fungicide))+
#    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
#    labs(x = "Proportion of grain yeild saved",
#    title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
#    theme(panel.grid.major = element_line(colour = "grey80"),
#          panel.grid.minor = element_line(colour = "grey50"),
#          panel.background = element_rect(fill = NA))+
#    guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
#    scale_x_continuous(limits = c(-0.2,0.55))
# 
#

#__________________________________________________________________________________________________________
# levels(factor(PM_MB_means$Fungicide))

# combine Sulphur treatments
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == "Sulphur" |
             Fungicide == "Sulphur (SC)" |
             Fungicide == "Sulphur (Ultra SC)" |
             Fungicide == "Sulphur (WP)")

unique(PM_MB_means2$spray_diff)

ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first Sulphur fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.3,0.6))

```
This plot shows that there is not a good probability that Sulphur will help save yield, even when it is sprayed at the ideal time.

```{r each_fungicide}
Chemical <- c("Amistar","Carbendazim","Tebeconazole", "propiconazole")
levels(factor(PM_MB_means$Fungicide))

# Generates multiple plots for each type of fungicide tested
for(Chem in Chemical){
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == Chem)

cat(Chem)

# the following code 'spray_group' sets the spray_diff groupings that are used in the plots
spray_group <- c(min(unique(PM_MB_means2$spray_diff))-1,
      -5, 5,
      max(unique(PM_MB_means2$spray_diff))+1)

spray_group < - c(sort(unique(PM_MB_means2$spray_diff)-1), max(unique(PM_MB_means2$spray_diff)))

print(spray_group)

p1 <- ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, spray_group)), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, spray_group)~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title=paste(Chem,"Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")))+
   scale_x_continuous(limits = c(-1,1))

print(p1)

}
```
It seems the calculation of spray diff does not elucidate any differences between application dates.
